%% ===========================================================================
%% TITLE PAGE (with author details) — submit as a SEPARATE file from the
%% anonymized manuscript (Information Processing & Management uses double-
%% anonymized review). Fill in the [[...]] placeholders before submission.
%% ===========================================================================
\documentclass[preprint,12pt]{elsarticle}
\usepackage{amssymb,amsmath}
\journal{Information Processing \& Management}

\begin{document}

\begin{frontmatter}

\title{When Learned Models Lose to Popularity: A Diagnosis of Patent
Technology-Transfer Demand Prediction under Realistic Evaluation}

%% --- Authors (match the order in the submission system; check spelling) ---
\author[hyis]{Sangwon Lee}
\author[hyme]{Kyungseok Lee\corref{cor1}}
\ead{bu5119@hanyang.ac.kr}
\author[hyme]{Jaewon Lee}
\author[lg]{Dongkyu Lee\corref{cor2}}
\ead{dongkyu44.lee@lge.com} %% [[confirm Dongkyu Lee's email]]

\affiliation[hyis]{organization={Division of International Studies, Hanyang University},
            city={Seoul},
            postcode={04763},
            country={Republic of Korea}}

\affiliation[hyme]{organization={School of Mechanical Engineering, Hanyang University},
            city={Seoul},
            postcode={04763},
            country={Republic of Korea}}

\affiliation[lg]{organization={Quantum AI Task, LG AI Lab, CTO Division, LG Electronics Co., Ltd.},
            addressline={19 Yangjae-daero 11-gil, Seocho-gu},
            city={Seoul},
            postcode={06772},
            country={Republic of Korea}}

\cortext[cor1]{Corresponding author.}
\cortext[cor2]{Corresponding author.}

\begin{abstract}
(The abstract is included in the anonymized manuscript file; it may be repeated
here or omitted on the title page per the editor's preference.)
\end{abstract}

\begin{keyword}
patent technology transfer \sep link prediction \sep graph neural networks \sep
popularity bias \sep cold-start \sep evaluation methodology
\end{keyword}

\end{frontmatter}

%% ===========================================================================
\section*{CRediT authorship contribution statement}
%% Edit to reflect actual contributions; remove roles that do not apply.
\textbf{Sangwon Lee:} Investigation, Data curation, Visualization,
Writing -- original draft.
\textbf{Kyungseok Lee:} Conceptualization, Methodology, Software, Formal analysis,
Writing -- original draft, Writing -- review \& editing.
\textbf{Jaewon Lee:} Software, Validation, Investigation.
\textbf{Dongkyu Lee:} Conceptualization, Supervision, Funding acquisition,
Writing -- review \& editing.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or
personal relationships that could have appeared to influence the work reported in
this paper.

\section*{Declaration of generative AI in the writing process}
%% Required by Elsevier if applicable; edit/remove as appropriate.
[[State whether and how generative AI tools were used, e.g., for language editing,
and confirm the authors reviewed and take full responsibility for the content. If
not used, remove this section.]]

\section*{Acknowledgements}
[[Funding sources (with grant numbers), language/writing help, and computing
resources. Do NOT place acknowledgements in the anonymized manuscript or as a
footnote to the title.]]

\section*{Data availability}
The KIPRIS patent data is obtained from the Korea Intellectual Property Rights
Information Service API (https://plus.kipris.or.kr); access requires a free API key,
and redistribution of the raw exports is subject to KIPRIS terms. The preprocessing
and evaluation code, experiment scripts, and an embedding-regeneration script are
released at [[repository URL / DOI]], enabling full reproduction of all tables and
figures from the KIPRIS exports.

\end{document}
